Untitled

### 2020-04-11 Rmd/Draft.Rmd
Adding metadata to draft

#let's select a unique network per coordinate
#Fix Bartomeus unp 2015
m[22,2] <- as.factor(-6.16895)
m[22,3] <- as.factor(37.234966)
#Dicks
m[22,2] <- as.factor(1.575532)
m[22,3] <- as.factor(52.762395)
#Dupont
m[22,2] <- as.factor(9.1)
m[22,3] <- as.factor(56.1)

>>>>

#let's select a unique network per coordinate
#Fix Bartomeus unp 2015
m[22,2] <- as.factor(-6.16895)
m[22,3] <- as.factor(37.234966)
#Dicks
m[27,2] <- as.factor(1.575532)
m[27,3] <- as.factor(52.762395)
#Dupont
m[28,2] <- as.factor(9.1)
m[28,3] <- as.factor(56.1)

### 2020-04-11 Rmd/Metadata_table.Rmd
Adding metadata to draft

#let's select a unique network per coordinate
#Fix Bartomeus unp 2015
m[22,2] <- as.factor(-6.16895)
m[22,3] <- as.factor(37.234966)
#Dicks
m[22,2] <- as.factor(1.575532)
m[22,3] <- as.factor(52.762395)
#Dupont
m[22,2] <- as.factor(9.1)
m[22,3] <- as.factor(56.1)

>>>>

m <- as.data.frame(m, stringsAsFactors = FALSE)
m$Longitude<- as.numeric(m$Longitude)
m$Latitude<- as.numeric(m$Latitude)

#let's select a unique network per coordinate
#Fix Bartomeus unp 2015
#m[22,2] <- as.numeric(-6.16895)
#m[22,3] <- as.factor(37.234966)
#Dicks
#m[27,2] <- as.factor(1.575532)
#m[27,3] <- as.factor(52.762395)
#Dupont
#m[28,2] <- as.factor(9.1)
m[28,3] <- as.numeric("56.1")
